\documentclass[a4paper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage[none]{hyphenat}
\setlength{\footskip}{3.60004pt}

\pagestyle{fancy}
\fancyhf{} % Clear header/footer
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\definecolor{darkblue}{rgb}{0.1, 0.1, 0.5}

\titleformat{\section}{\color{darkblue}\normalfont\large\bfseries\uppercase}{\thesection}{1em}{}
\titlespacing{\section}{0pt}{1.2em}{0.6em}

\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-4pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\sloppy

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \textbf{Viet Hai Nguyen}}\\[2pt]
    Eindhoven, The Netherlands \quad
    \faEnvelope~\href{mailto:viet.hai.nguyen@outlook.com}{viet.hai.nguyen@outlook.com} \quad
    \faPhone~+31 6 87777880 \\[2pt]
    \faGithub~\href{https://github.com/walhaihd}{github.com/walhaihd} \quad
    \faLinkedin~\href{https://linkedin.com/in/viet-hai-nguyen}{linkedin.com/in/viet-hai-nguyen}
\end{center}

%-----------PROFILE-----------
\section*{Profile}
Versatile software engineer with practical experience in building robust, user-friendly applications. Strong background in C\# and .NET, with a focus on clean code, automation, and real-world problem solving. Quick to learn, proactive in teams, and committed to delivering reliable solutions that scale.

%-----------EXPERIENCE-----------
\section*{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Morphotonics B.V.}{Jan 2022 -- Present}
    {Software Engineer}{Veldhoven, NL}
    \resumeItemListStart
      \resumeItem{Developed an OPC UA-based system for hardware communication and control.}
      \resumeItem{Created simulation tools to enable testing without physical hardware.}
      \resumeItem{Designed diagnostic dashboards with Blazor-ApexCharts to analyze hardware module performance after production cycles.}
      \resumeItem{Built an intuitive recipe editor to simplify machine setup for operators.}
      \resumeItem{Implemented a secure internal tool for remote deployments, reducing manual workload.}
      \resumeItem{Configured and maintained Ubuntu servers for production systems.}
      \resumeItem{Automated testing and deployment using Azure DevOps CI/CD pipelines.}
      \resumeItem{Collaborated with engineers and stakeholders to define features and support system rollout.}
      \resumeItem{\textbf{Technologies:} C\#, .NET 8, Blazor, OPC UA, MongoDB, MudBlazor, CI/CD, Ubuntu}
    \resumeItemListEnd

  \resumeSubheading
    {Smit Thermal Solutions B.V.}{Jul 2021 -- Dec 2021}
    {Junior Software Engineer}{Eindhoven, NL}
    \resumeItemListStart
      \resumeItem{Gathered system requirements and created UML diagrams to generate PLC code using Cordis Suite.}
      \resumeItem{Wrote and tested structured text code for B\&R PLC systems.}
      \resumeItem{Supported testing and commissioning by fixing bugs and adjusting control logic.}
      \resumeItem{\textbf{Technologies:} UML, Cordis Suite, Beckhoff PLC, B\&R PLC}
    \resumeItemListEnd

  \resumeSubheading
    {8vance}{Sep 2020 -- Feb 2021}
    {Graduation Intern}{Venlo, NL}
    \resumeItemListStart
      \resumeItem{Built a web interface to demonstrate a deep learning model that detects emotions in facial expressions.}
      \resumeItem{\textbf{Technologies:} Python, Django, OpenCV, Angular}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section*{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Fontys University of Applied Sciences}{Feb 2017 -- Feb 2021}
    {Bachelor of ICT \& Software Engineering}{The Netherlands}
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section*{Skills}
\resumeSubHeadingListStart
  \resumeSubItem{\textbf{Programming Languages:} C\#, Java, Python}
  \resumeSubItem{\textbf{Frameworks:} .NET 8, Blazor, MudBlazor}
  \resumeSubItem{\textbf{Tools:} Git, Azure DevOps, Azure Pipelines}
  \resumeSubItem{\textbf{Environments:} Ubuntu Server}
  \resumeSubItem{\textbf{Databases:} MongoDB, SQL Server, MySQL, SQLite}
  \resumeSubItem{\textbf{Core Skills:} Teamwork, Communication, Problem Solving, Adaptability}
\resumeSubHeadingListEnd

%-----------ADDITIONAL-----------
\section*{Additional Information}
\resumeSubHeadingListStart
  \resumeSubItem{\textbf{Languages:} English (Fluent), Dutch (A2), Vietnamese (Native)}
  \resumeSubItem{\textbf{Work Authorization:} Long-term EU residence permit}
\resumeSubHeadingListEnd

\end{document}
